# Missing Data
## Keith Swartz

```{r}
library(tidyverse)
library(VIM)
library(mice)
library(skimr)
```

```{r}
grades <- read_csv("class-grades.csv")
```


### Task 1

```{r}
skim(grades)
str(grades)
summary(grades)
```

There is missing data for the variables tutorial (1), midterm (3), takehome (3), and final (4).


### Task 2
```{r}
vim_plot = aggr(grades, numbers = TRUE, prop = c(TRUE, FALSE),cex.axis=.7)
```

Yes, there is one student that is missing both midterm and takehome scores.

### Task 3

```{r}
grades_rowdel<- grades %>% drop_na()
skim(grades_rowdel)
```

In the new data frame grades_rowdel, 89 rows remain.

### Task 4

```{r}
grades_coldel<- grades %>% select(-Final) 
grades_coldel<- select(grades_coldel,-TakeHome)
grades_coldel<- select(grades_coldel,-Midterm)
grades_coldel<- select(grades_coldel,-Tutorial)

```

Only two columns remain the the data frame grades_coldel after deleted all columns with missing data.

### Task 5

I would choose to use the row-wise deletion used in Task 4 because with this method we are only losing 10 observations out of 99 where as when we use column-wise deletion, we get rid of 4 very important variables where, at most, 4 observations are missing.

### Task 6

```{r}
set.seed(123) #sets seed for random number generator
imp_final = mice(grades, m=5, method='pmm', printFlag=FALSE)
#m is the number of imputations, 5 is a reasonable value as a default
#pmm is "predictive mean matching" = imputation method for numeric data
#printFlag reduces amount of output
summary(imp_final)

grades_complete = complete(imp_final) 
summary(grades_complete)
```

The mean value for the variable Final is 68.33.